Paper Visualizations

### 2022-05-27 eda/paper-graphics.Rmd
appendix 3 tables

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F)
library(tidyverse)
library(ggplot2)
library(boxr)
library(stargazer)
library(stringi)
box_auth()

#df <- box_read("949901868853", read_fun = readr::read_csv)
df <- read_csv("~/Box/Amicus IV/regressions/data for Amicus IV regressions/amicus-iv-regression-data-final-cases.csv") 
amicus <- box_read("947307207905", read_fun = readr::read_csv)
```

@@

```{r}
amici_ct_plt <- num_amici %>% 
  ggplot(., aes(x = year)) +
  geom_line(aes(y = cfemam, linetype = "Reproductive-Rights")) + 
  geom_line(aes(y = coppam, linetype = "Antiabortion")) + 
  scale_linetype_manual("Amici Type", values=c("Reproductive-Rights" = 1,"Antiabortion" = 2)) + 
  coord_cartesian(ylim = c(0, 50)) +
  labs(
    x = "Decision Year",
    y = "Average Number of Amici",
    title = "Annual Average Number of Amici for Abortion Cases"
  ) + 
  theme_minimal() +
  theme(
    plot.title = element_blank(),
    title = element_text(size = 10, family = "Times New Roman"),
    legend.text = element_text(size = 10, family = "Times New Roman"),
    axis.text = element_text(size = 10, family = "Times New Roman"),
    legend.position = "bottom"
  )

@@

# Table 2

@@

# Table 3

@@

# Table 4

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F, error = F)
library(tidyverse)
library(ggplot2)
library(interactions)
library(boxr)
library(stargazer)
library(stringi)
#box_auth()

#df <- box_read("949901868853", read_fun = readr::read_csv)
df <- read_csv("~/Box/Amicus IV/regressions/data for Amicus IV regressions/amicus-iv-regression-data-final-cases.csv") 
#amicus <- box_read("947307207905", read_fun = readr::read_csv)
```

@@

```{r}
amici_ct_plt <- num_amici %>% 
  ggplot(., aes(x = year)) +
  geom_line(aes(y = cfemam, linetype = "Reproductive-Rights")) + 
  geom_line(aes(y = coppam, linetype = "Antiabortion")) + 
  scale_linetype_manual("Amici Type:", values=c("Reproductive-Rights" = 1,"Antiabortion" = 2)) + 
  coord_cartesian(ylim = c(0, 50)) +
  labs(
    x = "Decision Year",
    y = "Average Number of Amici",
    title = "Annual Average Number of Amici for Abortion Cases"
  ) + 
  theme_minimal() +
  theme(
    plot.title = element_blank(),
    title = element_text(size = 10, family = "Times New Roman"),
    legend.text = element_text(size = 10, family = "Times New Roman"),
    axis.text = element_text(size = 10, family = "Times New Roman"),
    legend.position = "bottom"
  )

@@

# Table A.1

@@

# Table A.2

@@

# Table A.3

@@

# Justice ideology graphs

```{r}
data <- #box_read(final_cases) %>% 
  read_csv("~/Box/Amicus IV/regressions/data for Amicus IV regressions/amicus-iv-regression-data-final-cases.csv") %>% 
  filter(justicevot != "NA") %>% 
  mutate(justicevot = as.numeric(justicevot),
         justiceid = as.factor(justiceid),
         justicefem = as.factor(justicefem),
         nonftyp2 = as.factor(nonftyp2),
         lcdisdirfem = ifelse(lcdisdirfem==1, 0, 1),
         lcdisdirfem = as.factor(lcdisdirfem),
         #sgfem3 = as.factor(sgfem3), 
         cirsplit = as.factor(cirsplit)) %>% 
  mutate(across(c(forgauf_abortion_regret:forgauf_womens_health,
                  legauf_abortion_regret:legauo_womens_health,
                  lifauo_abortion_regret:medauo_womens_health,
                  relauf_abortion_regret:relauo_womens_health,
                  fem_abortion_regret:opp_womens_health),
                ~replace_na(.x, 0))) %>% 
  filter(case != "Gonzales v PP")

# add case ID (second level var)
case_ids <- data %>% distinct(case) %>% arrange(case) %>% mutate(id = 1:n())
data <- case_ids %>% left_join(., data, by = "case")

# scale
data <- data %>%
  select(case:cirsplit, pfemam, poppam,
         forgauf_abortion_regret:forgauf_womens_health,
         legauf_abortion_regret:legauo_womens_health,
         lifauo_abortion_regret:medauo_womens_health,
         relauf_abortion_regret:relauo_womens_health,
         fem_abortion_regret:opp_womens_health) %>%  
  mutate(across(c(where(is.numeric), -justicevot, -id, -cirsplit, -sgfem3),
                ~(scale(., center=T, scale=T))))
```

## Forg

Privacy

```{r}
forg_privacy_plt <- 
  interact_plot(forg_privacy_interactions, pred = forgauf_privacy, modx = justicemq,
                #modx.values = c(-3.5, -1, 0, 1, 3.5),
                # random
                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
                # quantiles
                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
                                "Moderately Conservative", "More Conservative"),
                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
                #outcome.scale = "link",
                x.label = "Frame Frequency (Scaled)",
                y.label = "Probability of Voting in Favor of Repro-Rights",
                legend.main = "Justice Ideology") +
  theme_minimal() +
  theme(
    plot.title = element_blank(),
    title = element_text(size = 10, family = "Times New Roman"),
    legend.text = element_text(size = 10, family = "Times New Roman"),
    axis.text = element_text(size = 10, family = "Times New Roman"))

ggsave("graphics/forg_privacy.png", forg_privacy_plt, height = 5, width = 8)

forg_privacy_plt
```

Undue Burden

```{r}
forg_undue_plt <- 
  interact_plot(forg_undue_interactions, pred = forgauf_undue_burden, modx = justicemq,
                #modx.values = c(-3.5, -1, 0, 1, 3.5),
                # random
                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
                # quantiles
                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
                                "Moderately Conservative", "More Conservative"),
                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
                #outcome.scale = "link",
                x.label = "Frame Frequency (Scaled)",
                y.label = "Probability of Voting in Favor of Repro-Rights",
                legend.main = "Justice Ideology") +
  theme_minimal() +
  theme(
    plot.title = element_blank(),
    title = element_text(size = 10, family = "Times New Roman"),
    legend.text = element_text(size = 10, family = "Times New Roman"),
    axis.text = element_text(size = 10, family = "Times New Roman"))

ggsave("graphics/forg_undue.png", forg_undue_plt, height = 5, width = 8)

forg_undue_plt
```

Women's Health

```{r}
forg_health_plt <- 
  interact_plot(forg_womenhealth_interactions, pred = forgauf_womens_health, modx = justicemq,
                #modx.values = c(-3.5, -1, 0, 1, 3.5),
                # random
                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
                # quantiles
                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
                                "Moderately Conservative", "More Conservative"),
                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
                #outcome.scale = "link",
                x.label = "Frame Frequency (Scaled)",
                y.label = "Probability of Voting in Favor of Repro-Rights",
                legend.main = "Justice Ideology") +
  theme_minimal() +
  theme(
    plot.title = element_blank(),
    title = element_text(size = 10, family = "Times New Roman"),
    legend.text = element_text(size = 10, family = "Times New Roman"),
    axis.text = element_text(size = 10, family = "Times New Roman"))

ggsave("graphics/forg_health.png", forg_health_plt, height = 5, width = 8)

forg_health_plt
```

Evidence

```{r}
forg_evidence_plt <- 
  interact_plot(forg_evidence_interactions, pred = forgauf_evidence, modx = justicemq,
                #modx.values = c(-3.5, -1, 0, 1, 3.5),
                # random
                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
                # quantiles
                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
                                "Moderately Conservative", "More Conservative"),
                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
                #outcome.scale = "link",
                x.label = "Frame Frequency (Scaled)",
                y.label = "Probability of Voting in Favor of Repro-Rights",
                legend.main = "Justice Ideology") +
  theme_minimal() +
  theme(
    plot.title = element_blank(),
    title = element_text(size = 10, family = "Times New Roman"),
    legend.text = element_text(size = 10, family = "Times New Roman"),
    axis.text = element_text(size = 10, family = "Times New Roman"))

ggsave("graphics/forg_evidence.png", forg_evidence_plt, height = 5, width = 8)

forg_evidence_plt
```

## RR Medical

Women's health

```{r}
medauf_health_plt <- 
  interact_plot(medauf_womenhealth_interactions, pred = medauf_womens_health, modx = justicemq,
                #modx.values = c(-3.5, -1, 0, 1, 3.5),
                # random
                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
                # quantiles
                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
                                "Moderately Conservative", "More Conservative"),
                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
                #outcome.scale = "link",
                x.label = "Frame Frequency (Scaled)",
                y.label = "Probability of Voting in Favor of Repro-Rights",
                legend.main = "Justice Ideology") +
  theme_minimal() +
  theme(
    plot.title = element_blank(),
    title = element_text(size = 10, family = "Times New Roman"),
    legend.text = element_text(size = 10, family = "Times New Roman"),
    axis.text = element_text(size = 10, family = "Times New Roman"))

ggsave("graphics/medauf_health.png", medauf_health_plt, height = 5, width = 8)

medauf_health_plt
```

## Prolife

Undue Burden

```{r}
lifauo_undue_plt <- 
  interact_plot(lif_undue_interactions, pred = lifauo_undue_burden, modx = justicemq,
                #modx.values = c(-3.5, -1, 0, 1, 3.5),
                # random
                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
                # quantiles
                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
                                "Moderately Conservative", "More Conservative"),
                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
                #outcome.scale = "link",
                x.label = "Frame Frequency (Scaled)",
                y.label = "Probability of Voting in Favor of Repro-Rights",
                legend.main = "Justice Ideology") +
  theme_minimal() +
  theme(
    plot.title = element_blank(),
    title = element_text(size = 10, family = "Times New Roman"),
    legend.text = element_text(size = 10, family = "Times New Roman"),
    axis.text = element_text(size = 10, family = "Times New Roman"))

ggsave("graphics/lifauo_undue.png", lifauo_undue_plt, height = 5, width = 8)

lifauo_undue_plt
```

## AA Medical

Expert-evidence

```{r}
medauo_evidence_plt <- 
  interact_plot(medauo_evidence_interactions, pred = medauo_evidence, modx = justicemq,
                #modx.values = c(-3.5, -1, 0, 1, 3.5),
                # random
                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
                # quantiles
                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
                                "Moderately Conservative", "More Conservative"),
                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
                #outcome.scale = "link",
                x.label = "Frame Frequency (Scaled)",
                y.label = "Probability of Voting in Favor of Repro-Rights",
                legend.main = "Justice Ideology") +
  theme_minimal() +
  theme(
    plot.title = element_blank(),
    title = element_text(size = 10, family = "Times New Roman"),
    legend.text = element_text(size = 10, family = "Times New Roman"),
    axis.text = element_text(size = 10, family = "Times New Roman"))

ggsave("graphics/medauo_evidence.png", medauo_evidence_plt, height = 5, width = 8)

medauo_evidence_plt
```

## AA Religious

Undue burden

```{r}
relauo_undue_plt <- 
  interact_plot(relauo_undue_interactions, pred = relauo_undue_burden, modx = justicemq,
                #modx.values = c(-3.5, -1, 0, 1, 3.5),
                # random
                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
                # quantiles
                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
                                "Moderately Conservative", "More Conservative"),
                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
                #outcome.scale = "link",
                x.label = "Frame Frequency (Scaled)",
                y.label = "Probability of Voting in Favor of Repro-Rights",
                legend.main = "Justice Ideology") +
  theme_minimal() +
  theme(
    plot.title = element_blank(),
    title = element_text(size = 10, family = "Times New Roman"),
    legend.text = element_text(size = 10, family = "Times New Roman"),
    axis.text = element_text(size = 10, family = "Times New Roman"))

ggsave("graphics/relauo_undue.png", relauo_undue_plt, height = 5, width = 8)

relauo_undue_plt
```

Fetus

```{r}
relauo_fetus_plt <- 
  interact_plot(relauo_fetus_interactions, pred = relauo_fetus, modx = justicemq,
                #modx.values = c(-3.5, -1, 0, 1, 3.5),
                # random
                #modx.values = c(-1.65, -.55, -.08, .35, 1.5),
                # quantiles
                modx.values = c(-3.4, -.75, -.3, .59, 1.9),
                modx.labels = c("More Liberal", "Moderately Liberal","Moderate",
                                "Moderately Conservative", "More Conservative"),
                colors = c("blue", "gray", "lightskyblue", "darksalmon", "red"),
                #outcome.scale = "link",
                x.label = "Frame Frequency (Scaled)",
                y.label = "Probability of Voting in Favor of Repro-Rights",
                legend.main = "Justice Ideology") +
  theme_minimal() +
  theme(
    plot.title = element_blank(),
    title = element_text(size = 10, family = "Times New Roman"),
    legend.text = element_text(size = 10, family = "Times New Roman"),
    axis.text = element_text(size = 10, family = "Times New Roman"))

ggsave("graphics/relauo_fetus.png", relauo_fetus_plt, height = 5, width = 8)

relauo_fetus_plt
```
